\artus{} -- A Framework for Event-based Data Analysis in High Energy Physics

### 2015-10-28 Core/doc/latex/paper.tex
Paper: Reorder citations

Following the structure of the CMSSW~\cite{cmssw} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
The basic concept of modules processing events within an event loop is complemented by tools for the configuration of every step.
The complete structure is explained in the next section.

@@

The \artus framework is written in C++.
The core of the framework only depends on the boost library\footnote{\url{http://www.boost.org}}.
Further dependencies may be introduced by the actual analysis code.
C++ is chosen for performance reasons and in order to be able to integrate existing frameworks and libraries that are commonly used in high energy physics.

>>>>

Following the structure of the CMS software framework~\cite{cms, cmssw}, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
The basic concept of modules processing events within an event loop is complemented by tools for the configuration of every step.
The complete structure is explained in the next section.

@@

The \artus framework is written in C++.
The core of the framework only depends on the boost library~\cite{boost}.
Further dependencies may be introduced by the actual analysis code.
C++ is chosen for performance reasons and in order to be able to integrate existing frameworks and libraries that are commonly used in high energy physics.
